\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-14 public/paper/pyg4ometry.tex
WILL have ill-defined behaviour.
Even if it ends up happening to work correctly, the behaviour itself can
still be ill-defined.

I don't think this is a too-strong thing to say either, as at the start of
this sentence we've already said that no RTMC codes can handle overlaps.

\subsection{Overlap detection}
All RTMC codes cannot handle spatial overlap between two geometric objects and are likely to have ill-defined behaviour when tracking particles  
through such a situation.  A key feature of \PYGEOMETRY{} is the detection of potential overlaps in a way which is most useful to the user, it does this by performing an intersection operation between solid instances and determining if the resultant mesh is empty. Figure~\ref{fig:overlap} shows the potential overlaps, a) protrusion of a daughter from the mother, b)  finite volume intersection between two daughters  and c) an overlap where two daughters share a face. If the resulting intersection 
is non-null then the overlaps can be displayed side-by-side in the visualisation. 
\begin{figure}[htbp]
\begin{center}
\includegraphics[width=8cm]{./diagrams/overlap.pdf}
\caption{Schematic of the three different types of overlap between daughters of a mother logical volume.}
\label{fig:overlap}
\end{center}
\end{figure}

>>>>

\subsection{Overlap detection}
All RTMC codes cannot handle spatial overlap between two geometric objects and will have ill-defined behaviour when tracking particles  
through such a situation.  A key feature of \PYGEOMETRY{} is the detection of potential overlaps in a way which is most useful to the user, it does this by performing an intersection operation between solid instances and determining if the resultant mesh is empty. Figure~\ref{fig:overlap} shows the potential overlaps, a) protrusion of a daughter from the mother, b)  finite volume intersection between two daughters  and c) an overlap where two daughters share a face. If the resulting intersection 
is non-null then the overlaps can be displayed side-by-side in the visualisation. 
\begin{figure}[htbp]
\begin{center}
\includegraphics[width=8cm]{./diagrams/overlap.pdf}
\caption{Schematic of the three different types of overlap between daughters of a mother logical volume.}
\label{fig:overlap}
\end{center}
\end{figure}
